%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref} % Add hyperref package for hyperlink functionality

\begin{document}

\introduction[
    fullname=Elilarasi S R,
    email=elilchandran@gmail.com,
    linkedin=https://linkedin.com/in/elilarasisr,
    github=https://github.com/Elilchandran,
    phone=8300887102,
    location=Chennai, % Use equal sign here, not colon
    portfolio=https://papaya-bubblegum-82bdad.netlify.app/,
]

\summary{Aspiring Full Stack Developer dedicated to creating innovative solutions. Actively seeking a key role in a reputable organization to apply my proficiency in JavaScript, React.js, and Node.js for impactful projects. Enthusiastic about contributing my expertise to achieve project objectives and align my professional growth with the success of the organization.}

\skills{
    \skillItem{Web Technologies}{JavaScript, HTML, CSS}
    \vspace{-0.5em}
    \skillItem{Frameworks / Libraries}{React.js, jQuery, AJAX, Node.js, Express.js, Bootstrap}
    \vspace{-0.5em}
    \skillItem{Databases}{MySQL, MongoDB}
    \vspace{-0.5em}
    \skillItem{Version Control \& Tools}{GitHub, Netlify, Render, API Integration similar to Clarifai, etc.}
    \vspace{-0.5em}
    \skillItem{Courses In Progress}{AWS (Amazon Web Services), Next.js}
}

\begin{workSection}{Projects}

\customItem[
    title={\href{https://frabjous-blancmange-3e1da0.netlify.app}{FACE DETECTION \& GENDER RECOGNITION -}},
    keyHighlight={
        \begin{itemize}
            \item Developed and designed my first \textbf{Front-end React} project using the \textbf{react-particles} library for particle animations.
            \vspace{-0.6em} % Adjust the value as needed
            \item Integrated the \textbf{Clarifai API} to successfully \textbf{detect faces and genders}, implementing custom functions for data retrieval and handling \textbf{image URLs}, resulting in a \textbf{vibrant display} with strategic skills. This is available on \href{https://github.com/Elilchandran/gender-demographics-recognition.git}{\textbf{GitHub}}.
            \vspace{0.6em} % Adjust the value as needed
        \end{itemize}
    }
]

\customItem[
    title={\href{https://celadon-twilight-cafa74.netlify.app/}{STUDENT TASK SUBMISSION PORTAL -}},
    keyHighlight={
        \begin{itemize}
            \item Developed a user-friendly portal using \textbf{React.js} for the \textbf{front-end}, \textbf{Node.js} for the \textbf{back-end}, and \textbf{MongoDB} for the \textbf{database}. This portal enhances fonts, icons, alongside various \textbf{charts}, using \textbf{Bootstrap/Material CSS, Chart.js}. The project demonstrates comprehensive skills in full-stack development.
            \vspace{-0.6em} % Adjust the value as needed
            \item Deployed \textbf{front-end} on \textbf{Netlify} and the \textbf{back-end} on \textbf{Render}. Both repositories are available on \textbf{GitHub} with separate \href{https://github.com/Elilchandran/project_name_frontend.git}{\textbf{front-end repository}} and \href{https://github.com/Elilchandran/project_name_backend.git}{\textbf{back-end repository}}, showcasing effective collaboration.
            \vspace{0.6em} % Adjust the value as needed
        \end{itemize}
    }
]

\customItem[
    title={\href{https://silver-squirrel-b4f7b3.netlify.app/}{MENTOR-STUDENT PORTAL -}},
    keyHighlight={
        \begin{itemize}
            \item Crafted an end-to-end project using \textbf{HTML JavaScript} for \textbf{front-end}, utilizing \textbf{DOM} for creating, assigning, and fetching students \& mentor. Implemented the back-end using \textbf{Node.js Express} and \textbf{MongoDB} for the database.
            \vspace{-0.6em} % Adjust the value as needed
            \item Successfully deployed the back-end on \textbf{Render} and the front-end on \textbf{Netlify}. Both repositories are available on \textbf{GitHub} with separate \href{https://github.com/Elilchandran/mentors_students_frontend.git}{\textbf{front-end repository}} and \href{https://github.com/Elilchandran/mentors_students.git}{\textbf{back-end repository}}, highlighting effective version control.
            \vspace{0.6em} % Adjust the value as needed
        \end{itemize}
    }
]

\customItem[
    title={\href{https://visionary-conkies-5130af.netlify.app/}{BOTCOMPANION HUB -}},
    keyHighlight={
        \begin{itemize}
            \item Created a responsive and visually appealing \textbf{RoboFriends} user interface using \textbf{React}, displaying user profiles. Integrated the \textbf{jsonplaceholder API} for seamless data retrieval.
            \vspace{-0.6em}
            \item Designed and implemented a robust search feature, enhancing user navigation and making it easy to find specific profiles within the application. The project source code is available on \href{https://github.com/Elilchandran/robot.git}{\textbf{GitHub}}.
            \vspace{0.6em}
        \end{itemize}
    }
]

\customItem[
    title={\href{https://sage-tulumba-48ad56.netlify.app/}{CHARACTER PORTFOLIO: THRONES EDITION -}},
    keyHighlight={
        \begin{itemize}
            \item Developed a dynamic character display using \textbf{HTML, CSS,} and \textbf{JavaScript}, leveraging \textbf{asynchronous functions} and fetching character data from the \textbf{ThronesAPI}.
            \vspace{-0.6em}
            \item Demonstrated proficiency in handling API requests, manipulating the DOM, and creating visually appealing user interfaces. The project is available on \href{https://github.com/Elilchandran/Game-of-Thrones.git}{\textbf{GitHub}}.
        \end{itemize}
    }
]

\end{workSection}
\vspace{0.3em} % Adjust the value as needed

\education{
    \educationItem[
        university=Guvi (Zen Class),
        college=An IIMA \& IITM incubated Company{,} Google For Education Partner,
        graduation=2023,
        grade=,
        program=Full Stack Developer Course,
    ]
    \educationItem[
        university=A.V.P. College of Arts and Science{,} Affiliated to Bharathiyar University{,} Coimbatore,
        graduation=2020,
        grade=First Class With Distinction,
        program=M.Com,
    ]
}
\vspace{-0.2em} % Adjust the value as needed
\begin{workSection}{Positions of Responsibility}

\customItem[
    keyHighlight={
        \begin{itemize}
            \item \textbf{Rotaract Club Coordinator} - District 3202 and \textbf{guided Leadership Training Programs} and Installation programs.
            \vspace{-0.6em} % Adjust the value as needed
            \item \textbf{Team Lead} - Poster Designing (Women's Empowerment) - Prize awarded by a reputed \textbf{news channel.}
            \vspace{-0.6em} % Adjust the value as needed
            \item \textbf{Guest Lecturer} for Two Years and presented various National and State Level seminars.
        \end{itemize}
    }
]

\end{workSection}

\end{document}
